---
title: "Batch Downloading Springer Free Books Using R"
author: Weiyang Tao (weiyangtao1513@gmail.com)
date: "`r Sys.Date()`"
output: 
  BiocStyle::html_document:
    highlight: pygments
    toc: true
    fig_width: 5
    number_sections: true
---
- - - - 
```{r, global_options, echo=FALSE, results="hide", eval=TRUE}
knitr::opts_chunk$set(collapse = TRUE, 
                      comment = "#>", 
                      fig.width = 5, 
                      fig.height = 4.5, 
                      fig.align = "center",
                      echo=TRUE, 
                      warning=FALSE, 
                      message=TRUE, 
                      tidy.opts=list(width.cutoff=80), 
                      tidy=FALSE)
rm(list = ls())
gc(reset = TRUE)
options(max.print = 200, width = 110)
```

# Introduction
[Springer](https://www.springer.com/) offers us many free books.
[Springer](https://www.springer.com/)  is part of Springer Nature, a global 
publisher that serves and supports the research community. It offers hundreds 
of thousands of books, part of which can be downloaded free. This note is to
show how to batch download about 400 free books using R.

# Loading libraries
```{r}
library(stringr)
library(httr)
```

# Reading the book URLs
A txt file called "SpringerBookURL.txt" is saved in 
[rawData](https://github.com/paodan/notebook/rawData). If you have 
clone/download the whole [notebook](https://github.com/paodan/notebook)
repository, you can run the following R code.
```{r}
x = read.csv("rawData/SpringerBookURL.txt", sep = "\t")
head(x)
```

The URLs listed above are the introduction pages of books. for example, the 
[URL](http://link.springer.com/openurl?genre=book&isbn=978-0-387-28117-9) of 
Developmental Neurobiology is:
http://link.springer.com/openurl?genre=book&isbn=978-0-387-28117-9,
while it's PDF downloading page is:
https://link.springer.com/content/pdf/10.1007%2F0-387-28117-7.pdf.

It seems there is no pattern between the two URLs. 
Actually http://link.springer.com/openurl?genre=book&isbn=978-0-387-28117-9 has 
been redirected to https://link.springer.com/book/10.1007%2F0-387-28117-7.
Then you can find the pattern of the pdf file URL and the introduction URL.

What you need to do is to use `httr` package to find the redirected URL.

# Batch downloading
By Running the following R code, you can download all books (roughly 8.5GB) to
`SpringerBooks` folder in you current working directory according to the 
`SpringerBookURL.txt` file.
```{r, eval=FALSE}
folder = "SpringerBooks"
dir.create(folder)
for(mi in seq_along(x$OpenURL)){
  cat(mi, ": ")
  # To get the real book URL
  url = GET(x$OpenURL[mi])$url
  
  # To get the pdf URL
  URL = paste0(sub("book", "content/pdf", url), ".pdf")
  
  # File name
  pdfFile = paste0(folder, "/", mi, "_", x$Book.Title[mi], ".pdf")
  
  # Download pdf file
  try(download.file(URL, pdfFile), silent = TRUE)
}
```

